Named Entity Recognition as Structured Prediction

### 2012-11-10 doc/report/paper.tex
+++

\documentclass[11pt]{article}
\usepackage{acl2011}
\usepackage[utf8]{inputenc}
\usepackage{linguex}
\usepackage{latexsym}  
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{verbatim}
\usepackage{array}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{qtree}
\usepackage{textcomp}

@@

\date{}

@@

\begin{abstract}
Named Entity Recognition is a task

@@

\subsection{Methods employed for NER}
For NER, there exist two general approaches: one is rule-based and the other statistical. 
Rule-based methods make use of the underlying rules governing a language to extract Named Entities. 
This approach, however, is rather high maintenance and requires extensive work by experts, such as computational linguists \cite{nadeau2007survey}.
The results can be quite high in precision, but lack considerably in recall. % rules are partly language-dependent

@@

\begin{table}[h!]
\begin{tabular}{| l | l |}
\hline
\bf Feature & \bf Example \\
\hline
Token &  \textbf{``Amsterdam''}\\
Suffix& Amster\textbf{dam}\\
Prefix&  \textbf{San} Sebastian\\
Captitalized& \textbf{B}enetton\\
Number Pattern & \\
UPPERCASE &  \textbf{BENETTON}\\
POS-tag &  Benetton \textbf{NNP}   \\
Lemma &  produced $\Rightarrow$ produce \\
\hline
\end{tabular}
\caption{Node Features}
\label{table:node}
\end{table}

@@

\section{Experiments and Evaluation}
In the following section, we present our experiments and the evaluation of our system.
\subsection*{Experiments}

\subsection*{Evaluation}
For the evaluation of the system we used \emph{Precision} and \emph{Recall} as shown in \ref{Precision} and \ref{Recall} respectively.
Precision is the percentage of Named Entities found by the system that are correct. Recall represents the the percentage of 
named entites present in the corpus that were found by the system. 
A named entity is only deemed correct if it is an exact match for the corresponding data file.
The general formula for the \emph{F-Score} is shown in \ref{Fscore}. Since we rate both \emph{Precision} and \emph{Recall} evenly, we 
use the harmonic mean as shown in \ref{F1}.

@@

\begin{table*}[t]
\centering
\begin{tabular}{| l | l l l| l l l |}

\hline
\bf Language & \multicolumn{3}{c|}{ \bf Test A}&\multicolumn{3}{c|}{ \bf Test B}\\
             & Precision & Recall & $F_1$ & Precision & Recall & $F_1$ \\ \hline
Spanish &       &          &     &          &               & \\
Dutch  &         &          &     &          &               &   \\
English &        &          &     &          &               &       \\
German &      &          &       &          &             & \\
\hline
\end{tabular}
\caption{NER Structured Prediction Results }
\label{table:Results}
\end{table*}

\section{Discussion of Results}

>>>>

\documentclass[11pt]{article}
\usepackage{acl2011}
\usepackage[utf8]{inputenc}
\usepackage{linguex}
\usepackage{latexsym}  
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{verbatim}
\usepackage{array}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{qtree}
\usepackage{textcomp}
\usepackage{placeins}
%\usepackage{float}

@@

\date{}
%\restylefloat{figure} 
%\restylefloat{table}

@@

\begin{abstract}
Named Entity Recognition is a fundamental task for a wide variety of
natural language processing applications, such as
question answering, information retrieval.

@@

\subsection{Methods employed for NER}
For NER, there exist two general approaches: one is rule-based and the other statistical. 
Rule-based methods make use of the underlying rules governing a language to extract Named Entities. 
This approach, however, is rather high maintenance and requires extensive work by experts, such as computational linguists \cite{nadeau2007survey}.
The results are quite reasonable, but not readily portable to other domains or languages. % rules are partly language-dependent

@@

\begin{table}[!h]
\begin{tabular}{| l | l |}
\hline
\bf Feature & \bf Example \\
\hline
Token &  \textbf{``Amsterdam''}\\
Suffix& Amster\textbf{dam}\\
Prefix&  \textbf{San} Sebastian\\
Captitalized& \textbf{B}enetton\\
Number Pattern & \\
UPPERCASE &  \textbf{BENETTON}\\
POS-tag &  Benetton \textbf{NNP}   \\
Lemma &  produced $\Rightarrow$ produce \\
\hline
\end{tabular}
\caption{Node Features}
\label{table:node}
\end{table}

@@

%\FloatBarrier 
\section{Experiments and Evaluation}
\begin{table*}[t!]
\scriptsize
\begin{tabular}{| l | l l l| l l l |}
\hline
\bf Language & \multicolumn{3}{c|}{ \bf Test A}&\multicolumn{3}{c|}{ \bf Test B}\\
             & Precision & Recall & $F_1$ & Precision & Recall & $F_1$ \\ \hline
Spanish &       &          &     &          &               & \\
Dutch  &         &          &     &          &               &   \\
English &        &          &     &          &               &       \\
German &      &          &       &          &             & \\
\hline
\end{tabular}
\caption{NER Structured Prediction Results }
\label{table:Results}
\end{table*}
In the following section, we present our experiments and the evaluation of our system.
\subsection*{Experiments}

\subsection*{Evaluation}

For the evaluation of the system we used \emph{Precision} and \emph{Recall} as shown in \ref{Precision} and \ref{Recall} respectively.
Precision is the percentage of Named Entities found by the system that are correct. Recall represents the the percentage of 
named entites present in the corpus that were found by the system. 
A named entity is only deemed correct if it is an exact match for the corresponding data file.
The general formula for the \emph{F-Score} is shown in \ref{Fscore}. Since we rate both \emph{Precision} and \emph{Recall} evenly, we 
use the harmonic mean as shown in \ref{F1}.

@@

\FloatBarrier
\section{Discussion of Results}
